---
title: "Installation Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installation_guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Install R-package

The package demand R 3.5.0 or later.

The project R package MCVCovLoc can be installed from GitHub:

To do this the package devtools are needed and can be installed from cran:
```{r eval = FALSE}
install.packages("devtools")
```

To install the MCVCovLoc package:
```{r eval = FALSE}
devtools::install_github("JensXII/MCVCovLoc", build_vignettes = TRUE)
```
For older version of R or devtools, this does not work e.g. the vignettes users_guide and install_guide are not build. Then try:
```{r eval = FALSE}
devtools::install_github("JensXII/MCVCovLoc", build_opts = c("--no-resave-data", "--no-manual"))
```

If this doesn't work either, you can download the source-code and install this:
- you may not be able to do this with Windows Explorer, but have to use Crome or another web-browser.

1. <https://github.com/JensXII/MCVCovLoc>

2. press 'Clone and download'

3. press 'Download ZIP'

4. unzip and save the downloaded to a designeded folder

5. in the folder double-click the MCVCovLoc R-project file

6. run:
```{r eval = FALSE}
devtools::install(build_vignettes = TRUE)
```
